Twisted 11-dimensional supergravity, I

### 2021-08-05 draft.tex
Linfty

\begin{lem}
The restricted action $I_{pot} = \Phi^* \til{I}_{BCOV}$ has $\CC^\times$ weight $+1$. 
In particular, the non-linear BRST operator 
\[
\delta_{pot} = Q_{pot} + \{I_{pot},-\}
\]
is $\CC^\times$ weight zero.
\end{lem}
\begin{proof}
The map $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$ preserves $\CC^\times$ weight, so it suffices to prove that $I_{BCOV}$ is weight $+1$. 
We will make use of two gradings on $\til{\cE}_{KS}$. 
The first is by holomorphic polyvector field type, and the second is by descendant degree.
The summand $u^l \PV^{k,\bu}$ is polyvector type $k$ and descendant degree $l$.

@@

>>>>

\begin{lem}
The restricted action $I_{pot} = \Phi^* \til{I}_{BCOV}$ has $\CC^\times$ weight $+1$. 
In particular, the non-linear BRST operator 
\[
\delta_{pot} = Q_{pot} + \{I_{pot},-\}
\]
is $\CC^\times$ weight zero.
\end{lem}
\begin{proof}
The map $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$ preserves $\CC^\times$ weight, so it suffices to prove that $\til{I}_{BCOV}$ is weight $+1$. 
We will make use of two gradings on $\til{\cE}_{KS}$. 
The first is by holomorphic polyvector field type, and the second is by descendant degree.
The summand $u^l \PV^{k,\bu}$ is polyvector type $k$ and descendant degree $l$.

@@

We describe the explicit $L_\infty$ automorphism $\Psi \colon (\cL_0)^{L_\infty} \rightsquigarrow (\cL_0)^{strict}$ intertwining the strict dg Lie structure on $\cL_0$ and this $L_\infty$ structure.
The linear term $\Psi^{(1)} = \id$ is the identity map. 
The higher terms $\Psi^{(n)}$ are defined by 
\begin{align*}
\Psi^{(n)} (\nu_1,\ldots, \nu_{n-k},\mu_1,\ldots, \mu_k) & = \delta_{k=2} \nu_1 \cdots \nu_{n-2} \mu_1 \mu_2 . \\
\end{align*}
\brian{someone check me}
